---
title: "P8105_hw5_sc5154"
author: "Shaohan Chen"
date: "2022-11-16"
output: github_document
---

This is the solution of P8105 Data Science Homework5.

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, message = FALSE)
```

```{r}
library(tidyverse)
```

## Problem 1

The goal of this problem is:

Create a tidy dataframe containing data from all participants, including the subject ID, arm, and observations over time.  
Then we make a spaghetti plot showing observations on each subject over time, and comment on differences between groups.

Let's start with loading the dataset.

```{r}
df = 
  tibble(
    file_name = list.files("./data/"),
    file_path = str_c("./data/", file_name)
   ) %>%
  mutate(data = map(file_path, read_csv)) %>%
  unnest()
```

Then let's tidy the dataset.

```{r}
df_par = 
  df %>%
  mutate(
    file_name = str_remove(file_name, ".csv"),
  ) %>%
  separate(file_name, into = c("arm", "subject_id"), sep = "_") %>%
  pivot_longer(
    cols = week_1:week_8,
    names_to = "week",
    names_prefix = "week_",
    values_to = "observation"
  )
```

Let's see how it looks like now
```{r}
head(df_par, 5)
```

Next, we make a spaghetti plot showing observations on each subject over time, and comment on differences between groups.

```{r}

```

